% \subsection{Glossary}
% \label{subsec:glossary}

Some insurance terms have more than one common meaning. To avoid possible misinterpretation the terms we have used in this report are defined below.
\begin{itemize}
\item \textbf{Premium Ultimate}: The projection of the total policy premiums. It is the sum of the Booked and Unsigned Premium minus the Return Premium, each defined below.
\item \textbf{Booked Premium}: The portion of written premium that has been paid to the insurer before the end of the reporting period.
\item \textbf{Return Premium}: The amount due to the insured if the actual cost of a policy is less than what the insured has previously paid. One common example of return premium is the profit commission, where insurers share a portion of their profits with the insured.
\item \textbf{Unsigned Premium}: Actuarial estimation of the remaining premium to be received after the reporting period for a given UWY and Line of business.
\item \textbf{Claims Ultimate}: Projection of total losses from claims. It is the sum of Paid Claims, Case Reserves, SIBNR and IBNR.
\item \textbf{Incurred Claims}: Sum of the Paid Claims and Case Reserve.
\item \textbf{Paid Claims}: The amount of money that has been paid by an insurer on behalf of insureds to cover the insureds’ claims.
\item \textbf{Case Reserve}: The estimate of unpaid loss amounts established by the claim department for unpaid claims that have been reported to the insurer. Claims reserves are typically established on an individual claim basis.
\item \textbf{Specific IBNR (SIBNR)} : Specific IBNR is part of IBNR Reserves. It relates to claims that have incurred and have been reported but no or not enough case reserves have been booked.
\item \textbf{IBNR} : IBNR Reserves includes provision for future development on known claims, claims that have been incurred and reported but not recorded, claims that are recorded as settled and are subsequently re-opened, claims that have been incurred but not reported and future claim events from policies that have already been written but have remaining exposure.
\item \textbf{Statutory Claims Ultimate} : The Statutory Claims Ultimate corresponds to the Claims Ultimate uplifted to account for inflation and including the PAD. It consists of the Statutory IBNR and the Case Reserves.
\item \textbf{PAD} : The Provision for Adverse Deviation (PAD) allows to add a level of conservatism to strengthen the reserves. It is based on the volatilities and expected values for Ultimate Loss ratios under the assumption that the reserves are following a log-normal distribution.
\item \textbf{Statutory IBNR}: The Statutory IBNR represents the IBNR and SIBNR Reserves with a loading of the PAD and inflation impacts. It is the amount of reserves booked by the finance team.
\end{itemize}
